Contribution Title\thanks{Supported by organization x.}

### 2019-10-24 paper/paper.tex
Unranked Tree Grammars

\paragraph{Automata}
An automata is a 5-tuple $(Q,\T,\delta,q_0,F)$, where $Q$ is a
finite set of states; $\T$ a finite set of terminals; $\delta$ a
transition function from $Q \times \T$ to finite subsets of $Q$
(or single states of $Q$ for a deterministic automaton);
$q_0 \in Q$ an initial state; and $F \subseteq Q$ a set of final
states.
%
A pushdown automata further adds a set of stack symbols $\Gamma$
and equips the transition function $\delta$ with information on
which symbols are pushed, popped or just read from the stack.

@@

The results and properties presented in this paper are more naturally described through unranked trees, thus all further references to trees are to unranked trees, despite ranked being more common in the literature. We further distinguish terminals used solely as leaves from terminals that may be either nodes or leaves. Since we will use unranked trees to represent parse trees, the former will represent terminals from the parsed word, while the latter represent terminals introduced as internal nodes.

>>>>

\paragraph{Automata}
An automata is a 5-tuple $(Q,\T,\delta,q_0,F)$, where $Q$ is a
finite set of states; $\T$ a finite set of terminals; $\delta$ a
transition function from $Q \times \T$ to finite subsets of $Q$
(or single states of $Q$ for a deterministic automaton);
$q_0 \in Q$ an initial state; and $F \subseteq Q$ a set of final
states.
%
A pushdown automata further adds a set of stack symbols $\Gamma$
and equips the transition function $\delta$ with information on
which symbols are pushed, popped or just read from the stack.
%
% TODO: Something on VPDAs?

\paragraph{Unranked Regular Tree Grammars}
Trees generalize words by allowing each terminal to have multiple
ordered successors, instead of just zero or one. In this paper, we
are only concerned with \emph{unranked} trees, where the arity of
a terminal is not fixed.
%
Each terminal with a non-zero rank has a label, allowing a
\emph{horizontal}
representation~\cite{comonTreeAutomataTechniques2007}. For
example, $a(n(\verb|'1'|) \;\verb|'+'|\; n(\verb|'2'|))$ represents
the parse tree of the string ``$1+2$''.
%
Finally, $yield : L(T) -> \T^{*}$ is the sequence of terminals
obtained by a left-to-right traversal of a tree. Informally, it is
the flattening of a tree after all internal nodes have been
removed.

@@

The results and properties presented in this paper are more naturally described through unranked trees, thus all references to trees here are to unranked trees, despite ranked being more common in the literature. We further distinguish terminals used solely as leaves from terminals that may be either nodes or leaves. Since we will use unranked trees to represent parse trees, the former will represent terminals from the parsed word, while the latter represent terminals introduced as internal nodes.
